An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-17 draft.tex
images

\usepackage{lineno,hyperref}

@@

% This paragraph will be moved to the Proposed Method section - Mario
% Based on a reactive architecture \cite{guervos2018introducing} , each
% subpopulation is represented as an event message that is pushed asynchronously
% into a message queue. Incoming messages trigger stateless functions that receive
% the subpopulation and proceed to run an algorithm, using the parameters and
% population included in the message. After the specified number of iterations,
% each stateless function returns the evolved subpopulation by again pushing a
% message to another queue, used for receiving the resulting subpopulations.
% Subpopulations are received from the queue by a controller that is responsible
% for mixing the individuals from different subpopulations and producing new
% subpopulations. These new subpopulations are pushed again by the controller into
% the message queue, creating a loop. The cycle stops when the controller receives
% a subpopulation containing a candidate solution that satisfies a particular
% condition, or a maximum number of messages were received.

@@

\section{Proposed Method} 
\label{method}

>>>>

\usepackage{lineno,hyperref}
\graphicspath{ {./images/} }

@@

@@

\section{Proposed Method} 
\label{method}
This paragraph will be moved to the Proposed Method section - Mario
Based on a reactive architecture \cite{guervos2018introducing} , each
subpopulation is represented as an event message that is pushed asynchronously
into a message queue. Incoming messages trigger stateless functions that receive
the subpopulation and proceed to run an algorithm, using the parameters and
population included in the message. After the specified number of iterations,
each stateless function returns the evolved subpopulation by again pushing a
message to another queue, used for receiving the resulting subpopulations.
Subpopulations are received from the queue by a controller that is responsible
for mixing the individuals from different subpopulations and producing new
subpopulations. These new subpopulations are pushed again by the controller into
the message queue, creating a loop. The cycle stops when the controller receives
a subpopulation containing a candidate solution that satisfies a particular
condition, or a maximum number of messages were received.

\subsection{Event Driven Model} 
\label{edm}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{kafkEO}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
\end{figure}

\subsection{Workers} 
\label{edm}

\subsection{Controller} 
\label{edm}

\subsection{Experimental Process} 
\label{edm}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{experiment_flow}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{worker}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
\end{figure}
